Time for a rethink: time sub-sampling methods in disparity-through-time analyses

### 2017-12-20 manuscript/time-slice-appendices.tex
Tidied up appendices

% Preamble
\documentclass[12pt,a4paper]{article}
\usepackage{enumerate} 	
\usepackage{setspace}						
\usepackage{authblk}	
\usepackage{graphicx} 	
%\usepackage[nomarkers, nolists]{endfloat} 
\usepackage{pdflscape}	
\usepackage{mathtools}	
\usepackage[osf]{mathpazo} 
\usepackage{lineno} 	
\usepackage{hyperref}
\usepackage[round]{natbib} 
\usepackage{setspace}
\usepackage{longtable}

\setcounter{secnumdepth}{0} 
\raggedright 			
\pagenumbering{arabic}

@@

\noindent{\Large \bf Supporting Information from ``Time for a rethink: time sub-sampling methods in disparity-through-time analyses''}

\raggedright
\setlength{\parindent}{1cm}

@@

\subsection{Brusatte2014 (Figure \ref{figure:brusatte})} 
We used one randomly selected time-scaled tree from Brusatte et al. (2014).
Zero-length branches were replaced with the minimum branch length in the phylogeny.
The following taxa were removed because they were in the phylogeny but not the character matrix or vice versa: \textit{Sinraptor dongi}, \textit{Hesperonychus elizabethae}, \textit{Pyroraptor olympius}, \textit{Limenavis patagonica}, \textit{Lithornis}, \textit{Crypturellus undulatus}, \textit{Gallus gallus}, \textit{Crax pauxi}, \textit{Anas platyrhynchus}, \textit{Chauna torquata}, \textit{Epidendrosaurus} and \textit{Kinnareemimus}. 
The following taxa were removed because they shared no characters in the morphological matrix: \textit{Shanag ashile}, \textit{Atrociraptor marshalli}, \textit{Proceratosaurus bradleyi}, \textit{Incisivosaurus gauthieri}, \textit{Enigmosaurus}, \textit{Nanshiungosaurus brevispinus}, \textit{Xixiasaurus}, \textit{Tsaagan mangas}, \textit{Mirischia}, \textit{Pedopenna}, \textit{Suzhousaurus}, \textit{Juratyrant}, \textit{Vorona}, \textit{Bonapartenykus}, \textit{Teratophoneus}, \textit{Gobipteryx}, \textit{Songlingornis}, \textit{Liaoningornis longidigitu} and \textit{Achillesaurus}.

@@

% disparity peaks figures
\begin{figure}[!htbp]
    \centering
    \includegraphics[width=1\linewidth, height=1\textheight, keepaspectratio]{figures/fig-peaks-epoch-appendix.pdf}
    \caption[Timing of peak disparity for four example datasets.]
    {Timing of peak disparity for stratigraphic epochs.
    Median bootstrapped disparities were calculated using time binning and time-slicing approaches. 
    Stratigraphy uses unequal time bins or non-equidistant time-slices, where the width of the bin, or the interval between slices, is equivalent to stratigraphic epochs. 
    Duration uses equal time bins or equidistant time-slices, where the width of the bin, or the interval between slices, is the average duration of stratigraphic epochs in the time frame of the dataset. 
    Number uses equal time bins or equidistant time-slices, where the number of bins, or the number of slices, is the average number of stratigraphic epochs in the time frame of the dataset. 
    For time bins there are two points indicating the maximum and minimum ages of the time bin within which peak disparities appeared.
    The four datasets are on separate rows, from top to bottom these are Beck2014, Brusatte2014, Bapst2016 and Wright2017 (see Table 1 for details).
    Results for stratigraphic ages are in Figure A4.}
    \label{figure:peak2}
  \end{figure}

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=1\linewidth, height=1\textheight, keepaspectratio]{figures/fig-peaks-age-appendix.pdf}
    \caption[Timing of peak disparity for four example datasets.]
    {Timing of peak disparity for stratigraphic ages.
    Median bootstrapped disparities were calculated using time binning and time-slicing approaches. 
    Stratigraphy uses unequal time bins or non-equidistant time-slices, where the width of the bin, or the interval between slices, is equivalent to stratigraphic ages. 
    Duration uses equal time bins or equidistant time-slices, where the width of the bin, or the interval between slices, is the average duration of stratigraphic ages in the time frame of the dataset. 
    Number uses equal time bins or equidistant time-slices, where the number of bins, or the number of slices, is the average number of stratigraphic ages in the time frame of the dataset. 
    For time bins there are two points indicating the maximum and minimum ages of the time bin within which peak disparities appeared.
    The four datasets are on separate rows, from top to bottom these are Beck2014, Brusatte2014, Bapst2016 and Wright2017 (see Table 1 for details).
    Results for stratigraphic epochs are in Figure A3.}
    \label{figure:peak3}
  \end{figure}

>>>>

% Preamble
\documentclass[12pt,a4paper]{article}
\usepackage{enumerate} 	
\usepackage{setspace}						
\usepackage{authblk}	
\usepackage{graphicx} 	
%\usepackage[nomarkers, nolists]{endfloat} 
\usepackage{pdflscape}	
\usepackage{mathtools}	
\usepackage[osf]{mathpazo} 
\usepackage{lineno} 	
\usepackage{hyperref}
\usepackage[round]{natbib} 
\usepackage{setspace}
\usepackage{longtable}
\usepackage{fancyhdr}

\setcounter{secnumdepth}{0} 
%\raggedright 			
%\pagenumbering{arabic}	
\pagenumbering{gobble}

\pagestyle{fancy}
\rhead{\textit{Guillerme \& Cooper 2018}}
\lhead{\textit{Supporting Information}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\headsep}{0.3in}

@@

\par{\centering{\Large \bf Supporting Information from ``Time for a rethink: time sub-sampling methods in disparity-through-time analyses''\par}}

\setlength{\parindent}{1cm}

@@

\subsection{Brusatte2014 (Figure \ref{figure:brusatte})} 
We used one randomly selected time-scaled tree from Brusatte et al. (2014).
Zero-length branches were replaced with the minimum branch length in the phylogeny.
The following taxa were removed because they were in the phylogeny but not the character matrix or vice versa: \textit{Sinraptor dongi}, \textit{Hesperonychus elizabethae}, \textit{Pyroraptor olympius}, \textit{Limenavis patagonica}, \textit{Lithornis}, \textit{Crypturellus undulatus}, \textit{Gallus gallus}, \textit{Crax pauxi}, \textit{Anas}\\ \textit{platyrhynchus}, \textit{Chauna torquata}, \textit{Epidendrosaurus} and \textit{Kinnareemimus}. 
The following taxa were removed because they shared no characters in the morphological matrix: \textit{Shanag ashile}, \textit{Atrociraptor marshalli}, \textit{Proceratosaurus bradleyi}, \textit{Incisivosaurus gauthieri}, \textit{Enigmosaurus}, \textit{Nanshiungosaurus brevispinus}, \textit{Xixiasaurus}, \textit{Tsaagan mangas}, \textit{Mirischia}, \textit{Pedopenna}, \textit{Suzhousaurus}, \textit{Juratyrant}, \textit{Vorona}, \textit{Bonapartenykus}, \textit{Teratophoneus}, \textit{Gobipteryx}, \textit{Songlingornis}, \textit{Liaoningornis longidigitu} and \textit{Achillesaurus}.

@@

% disparity peaks figures
\begin{figure}[!htbp]
    \centering
   % \includegraphics[width=1\linewidth, height=1\textheight, keepaspectratio]{figures/fig-peaks-epoch-appendix.pdf}
    \caption[Timing of peak disparity for four example datasets.]
    {Timing of peak disparity for stratigraphic epochs.
    Median bootstrapped disparities were calculated using time binning and time-slicing approaches. 
    Stratigraphy uses unequal time bins or non-equidistant time-slices, where the width of the bin, or the interval between slices, is equivalent to stratigraphic epochs. 
    Duration uses equal time bins or equidistant time-slices, where the width of the bin, or the interval between slices, is the average duration of stratigraphic epochs in the time frame of the dataset. 
    Number uses equal time bins or equidistant time-slices, where the number of bins, or the number of slices, is the average number of stratigraphic epochs in the time frame of the dataset. 
    For time bins there are two points indicating the maximum and minimum ages of the time bin within which peak disparities appeared.
    The four datasets are on separate rows, from top to bottom these are Beck2014, Brusatte2014, Bapst2016 and Wright2017 (see Table 1 for details).
    Results for stratigraphic ages are in Figure A4.}
    \label{figure:peak2}
  \end{figure}

\begin{figure}[!htbp]
    \centering
    %\includegraphics[width=1\linewidth, height=1\textheight, keepaspectratio]{figures/fig-peaks-age-appendix.pdf}
    \caption[Timing of peak disparity for four example datasets.]
    {Timing of peak disparity for stratigraphic ages.
    Median bootstrapped disparities were calculated using time binning and time-slicing approaches. 
    Stratigraphy uses unequal time bins or non-equidistant time-slices, where the width of the bin, or the interval between slices, is equivalent to stratigraphic ages. 
    Duration uses equal time bins or equidistant time-slices, where the width of the bin, or the interval between slices, is the average duration of stratigraphic ages in the time frame of the dataset. 
    Number uses equal time bins or equidistant time-slices, where the number of bins, or the number of slices, is the average number of stratigraphic ages in the time frame of the dataset. 
    For time bins there are two points indicating the maximum and minimum ages of the time bin within which peak disparities appeared.
    The four datasets are on separate rows, from top to bottom these are Beck2014, Brusatte2014, Bapst2016 and Wright2017 (see Table 1 for details).
    Results for stratigraphic epochs are in Figure A3.}
    \label{figure:peak3}
  \end{figure}
